Figures main manuscript

### 2019-11-26 code/figures.rmd
Added Risk differences to Fig 3 and plot clarifications

```{r Plot_tau_against_I2, fig.asp = 0.618, cache = TRUE}
dat3 <- readRDS("../data/tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

```{r Density-plot-prep, cache = TRUE}
#1) I2 plot----
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

@@

##Figure 3, correlations per effect type

```{r corr_per_effect_type-prep, cache = TRUE}
#Each set of input datapoints is meta-analyzed as per the original replication project
#Then correlated with tau2 per effect type
#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

@@

OR_fit <- function(x){
    fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
}

@@

ml2_or <- c("Affect & Risk", "Trolley Dilemma 1", "Framing", "Trolley Dilemma 2") #odds ratio effects in ML2 we will fit as OR

odds_ratios <- dat %>% 
  filter(effect %in% c(OR2d, ml2_or)) %>% 
  split(.$effect) %>% 
  map_dfr(OR_fit, .id = "effect")

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% #get unique rows
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference")) %>% 
  left_join(tau2_per_type) %>% #Add the meta-analytic results
  filter(!effect %in% c(odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
  bind_rows(MD_standardized) %>% #add MD after standardization
  bind_rows(odds_ratios) %>% #add odds ratios
  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
         effect_type = ifelse(effect %in% odds_ratios$effect, "Odds Ratio", effect_type),
         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
  filter(effect_type %in% c("Standardized Mean Difference", "Odds Ratio"))

@@

```{r corr_per_effect_type-plot, cache = FALSE}
#tau2plot----
tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#I2plot----
I2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = s_I2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_x_continuous(name = "Effect size") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#H2plot----
H2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

Figure 3. The correlation between effect size and A) tau2, B) I2 and C) H2 respectively 40 effects that were measured as mean or standardized mean differences and 8 effects measured as odds ratios from 13 pre-registered multi-lab replication projects. Effects reported as mean differences were standardized. Square brackets contain 95% bootstrapped percentile confidence intervals.

>>>>

```{r Plot_tau_against_I2, fig.asp = 0.618}
dat3 <- readRDS("../data/tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

```{r Density-plot-prep}
#1) I2 plot----
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

@@

## Figure 3, correlations per effect type

```{r corr_per_effect_type-prep}
#Each set of input datapoints is meta-analyzed as per the original replication project
#Then correlated with tau2 per effect type
#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

@@

log_or_fit <- function(x){ #NB! if a cell is 0, 1/2 will be added to it
    fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
}

@@

#odds ratio effects in ML2 we will fit as OR
ml2_or <- c("Affect & Risk", "Trolley Dilemma 1", "Framing", "Trolley Dilemma 2")

#Risk differences from RRR1 that can be fit as odds ratios as well
rd_effects <- c("Verbal overshadowing 1", "Verbal overshadowing 2")

log_odds_ratios <- dat %>% 
  filter(effect %in% c(OR2d, ml2_or, rd_effects)) %>% 
  split(.$effect) %>% 
  map_dfr(log_or_fit, .id = "effect")

#One with NA values: ML2; Trolley dilemma 1; Site = 'cas'

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% #get unique rows
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference")) %>% 
  left_join(tau2_per_type) %>% #Add the meta-analytic results
  filter(!effect %in% c(log_odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
  bind_rows(MD_standardized) %>% #add MD after standardization
  bind_rows(log_odds_ratios) %>% #add odds ratios
  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
         effect_type = ifelse(effect %in% log_odds_ratios$effect, "Log Odds Ratio", effect_type),
         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
  filter(effect_type %in% c("Standardized Mean Difference", "Log Odds Ratio"))

@@

```{r corr_per_effect_type-plot, cache = FALSE}
#tau2plot----
tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between Studies Variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#I2plot----
I2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = s_I2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#H2plot----
H2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

Figure 3. The correlation between absolute effect size and A) tau2, B) I2 and C) H2 respectively for 40 effects that were measured as mean or standardized mean differences and 8 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects. Effects reported as mean differences were standardized and risk differences computed as log odds ratios. Square brackets contain 95% bootstrapped percentile confidence intervals.
